Quantum Magic Games

### 2023-07-03 paper/main.tex
paper => fix third column
paper => hypergraphs

\usepackage{tikz}
\usetikzlibrary{quantikz2}

@@

\begin{document}
\title{Quantum Pseudo-Telepathy}
\subtitle{The Magic Square Game}

@@

Example~\ref{ex:classic-sol} illustrates one of the many deterministic
strategies that Alice and Bob can adopt. It is not difficult to
convince yourself that, no matter how they decide to fill in
their entries, it is impossible for them to come up with predefined
answers that always win. Any deterministic strategy is a pair of
matrices, one for Alice and another for Bob. The only way that they could
design a strategy that wins with certainty every round is to prepare two
identical matrices satisfying the requirements for each row and for each
column. That is, a single matrix for which the product of every row is
\(+1\) and the product of every column is \(-1\). Such a matrix cannot
possibly exist! It turns out that the best that they can do is to win
with probability \(\nicefrac{8}{9}\).

What if Alice and Bob decide for a probabilistic strategy? That is, Alice and
Bob each carry a coin. When assigned a row/column, they flip their
coins and fill the entries of the row/column based on the outcomes of
the coins. Can they do better? To randomly assign values to one row
(equivalently, one column) is essentially the same as randomly
selecting one of the \(2^{9}\) possible predefined \(3 \times 3\)
grids (including those matrices that would lead to invalid
answers). In other words, a probabilistic strategy for the Magic
Square game is one in which Alice and Bob randomly select a
deterministic strategy. Hence, no matter how lucky Alice and Bob are,
the probability of success of any strategy that they come up with is
bounded by the winning probability of the best deterministic strategy,
which is \(\nicefrac{8}{9}\). Theorem~\ref{thm:classical-success}
formalizes this argument.

@@

\section{Quantum Unitaries (? research)}
\label{sec:quantum-unitaries}

\printbibliography{}
\end{document}

>>>>

\usepackage{tikz}
\usetikzlibrary{intersections}
\usetikzlibrary{calc}
\usetikzlibrary{quantikz2}

@@

\begin{document}
\title{Quantum Magic Games}

@@

Example~\ref{ex:classic-sol} illustrates one of the many deterministic
strategies that Alice and Bob can adopt. It is not difficult to
convince yourself that, no matter how they decide to fill in their
entries, it is impossible for them to come up with predefined answers
that always win. Any deterministic strategy is a pair of matrices, one
for Alice and another for Bob. The only way that they could design a
strategy that wins with certainty every round is to prepare two
identical matrices satisfying the requirements for each row and for
each column. That is, a single matrix for which the product of every
row is \(+1\) and the product of every column is \(-1\). Such a matrix
cannot possibly exist!  To see that, consider the constraints over
each row and column:
\[\begin{aligned}
    m_{0,0}\, m_{0,1}\, m_{0,2} &= +1 \\
    m_{1,0}\, m_{1,1}\, m_{1,2} &= +1 \\
    m_{2,0}\, m_{2,1}\, m_{2,2} &= +1 \\
    m_{0,0}\, m_{1,0}\, m_{2,0} &= -1 \\
    m_{0,1}\, m_{1,1}\, m_{2,1} &= -1 \\
    m_{0,2}\, m_{1,2}\, m_{2,2} &= -1 \\
    \midrule
    +1 &\neq -1
  \end{aligned}\]

It turns out that the best that they can do is to win
with probability \(\nicefrac{8}{9}\)

What if Alice and Bob decide for a probabilistic strategy? That is, Alice and
Bob each carry a coin. When assigned a row/column, they flip their
coins and fill the entries of the row/column based on the outcomes of
the coins. Can they do better? To randomly assign values to one row
(equivalently, one column) is essentially the same as randomly
selecting one of the \(2^{9}\) possible predefined \(3 \times 3\)
grids (including those matrices that would lead to invalid
answers). In other words, a probabilistic strategy for the Magic
Square game is one in which Alice and Bob randomly select a
deterministic strategy. Hence, no matter how lucky Alice and Bob are,
the probability of success of any strategy that they come up with is
bounded by the winning probability of the best deterministic strategy,
which is \(\nicefrac{8}{9}\). A formal proof is given in~\ref{xxx}
for any pseudo-telepathy game (i.e.\ games whose quantum strategies
exhibit this notion of pseudo-telapathy).

@@

\section{Characterizing Quantum Magic Games}
\label{sec:extending}
What if we change the format of the Mermin-Peres magic square game?
Maybe increase the number of rows and columns, or even change the
shape entirely? Figure~\ref{fig:as-graph} (a) gives an example of the
magic pentagram game, in which the product of the labels (\(+1\) or
\(-1\)) assigned to each of four vertices in a line must equal the
labels of that line (the product of the four vertices in the topmost
horizontal line, for example, must be \(-1\)). Notice that we are now
changing the visualization format to
hypergraphs. Figure~\ref{fig:as-graph} (b) shows the magic square as a
hypergraph. In this section, we explore a characterization of games that
follow the same style as the magic square and pentagram, given
by~\ref{arkhipov2012}.

\begin{figure}[htbp]
  \centering
  \begin{subfigure}[t]{0.49\textwidth}
    \begin{center}
      \begin{tikzpicture}[vertex/.style={circle, thin, fill=blue!30, draw, inner sep=0, minimum size=5pt}]
        \node (00) [vertex] at (-1.25, 0) {};
        \node (01) [vertex] at (0,  0) {};
        \node (02) [vertex] at (1.25,  0) {};

        \node (10) [vertex] at (-1.25, -1.25) {};
        \node (11) [vertex] at (0,  -1.25) {};
        \node (12) [vertex] at (1.25,  -1.25) {};

        \node (20) [vertex] at (-1.25, -2.5) {};
        \node (21) [vertex] at (0,  -2.5) {};
        \node (22) [vertex] at (1.25, -2.5) {};

        \node (r0) [text=green!50!black!80] at (1.65, -0.05) {\(+1\)};
        \node (r1) [text=green!50!black!80] at (1.65, -1.20) {\(+1\)};
        \node (r2) [text=green!50!black!80] at (1.65, -2.45) {\(+1\)};

        \node (c0) [text=red!50!black!80] at (-1.2, -2.8) {\(-1\)};
        \node (c1) [text=red!50!black!80] at (-0.05, -2.8) {\(-1\)};
        \node (c2) [text=red!50!black!80] at (1.2, -2.8) {\(-1\)};

        \path[]
        (00) edge (01) edge (10)
        (01) edge (02) edge (11)
        (02) edge (12)

        (10) edge (11) edge (20)
        (11) edge (12) edge (21)
        (12) edge (22)

        (20) edge (21)
        (21) edge (22)
        ;
      \end{tikzpicture}
    \end{center}
    \caption{The magic square game as a hypergraph.}
  \end{subfigure}
  \hfill{}
   \begin{subfigure}[t]{0.49\textwidth}
    \begin{center}
      \begin{tikzpicture}[vertex/.style={circle, thin, fill=blue!30, draw, inner sep=0, minimum size=5pt}]
        \foreach \c [evaluate=\c as \ang using {18 + 72*\c}] in {0, 1, 2, 3, 4} {
          \node [vertex] (\c) at (\ang:25mm) {};
        }

        \draw [name path=0--2] (0) -- (2);
        \draw [name path=0--3] (0) -- (3);
        \draw [name path=1--3] (1) -- (3);
        \draw [name path=1--4] (1) -- (4);
        \draw [name path=2--4] (2) -- (4);

        \node [vertex] (01) at (intersection of 0--2 and 1--4) {};
        \node [vertex] (04) at (intersection of 0--3 and 1--4) {};
        \node [vertex] (12) at (intersection of 1--3 and 0--2) {};
        \node [vertex] (23) at (intersection of 1--3 and 2--4) {};
        \node [vertex] (34) at (intersection of 0--3 and 2--4) {};

        \node [text=red!50!black!80] (label0--2) at ($(01)!0.5!(12) - (0, 0.25)$) {\(-1\)};
        \node [text=green!50!black!80] (label1--4) at ($(01)!0.5!(04) + (-0.3, -0.1)$) {\(+1\)};
        \node [text=green!50!black!80] (label0--3) at ($(04)!0.5!(34) + (-0.1, 0.25)$) {\(+1\)};
        \node [text=green!50!black!80] (label2--4) at ($(23)!0.5!(34) + (+0.1, 0.25)$) {\(+1\)};
        \node [text=green!50!black!80] (label1--3) at ($(12)!0.5!(23) + (+0.3, -0.1)$) {\(+1\)};
      \end{tikzpicture}
    \end{center}
    \caption{The pentagram game as a hypergraph.}
  \end{subfigure}
  \caption{Examples of hypergraphs representing quantum magic games~\ref{arkhipov2012}.}
\end{figure}
\printbibliography{}
\end{document}
